Usability of Modern Display Technologies

### 2014-10-13 mental-model-paper/paper2.tex
first part of background section complete

It is significant to study electronic screens in the field of \textit{human-computer interaction} (HCI) as they are the devices through which information is transferred between the users and the interface. Although electronic displays have been around for nearly a century, they are still transforming and evolving in a multitude of ways. Screens are diversifying in order to tackle  the limitations that have presented themselves over the years. Screen devices have been changing in a variety of ways---including altering in size, shape, flexibility, resolution, and more---in order to increase usability for specific tasks.

There exists a plethora of different kinds of screen devices, each designed and built for particular functions. For example, \textit{focus plus context screens} (f+c screens), which are wall-size low-resolution displays with an embedded high-resolution display region, are currently a proposed solution to working with visual documents that are too large to fit standard screens.\cite{Baudisch:2002:FPC:506443.506445} Another kind of screen that is emerging is the \textit{BiDirectional (BiDi) Screen}, which is a thin, depth-sensing liquid-crystal display (LCD) that allows for 3D interaction using light fields.\cite{Hirsch:2009:BST:1618452.1618505}

 Though each kind of screen has its merits, this study will focus exclusively on touch sensitive screens. Many experts within the field of interaction design have discussed how the concepts of the field map specifically to the usability of touch sensitive screens. Researchers from Linköping University articulated how ``interaction design on touch sensitive screens is literally the most `direct' form of HCI, where information display and control are but one surface".\cite{Albinsson:2003:HPT:642611.642631}

\section{Background/ Prior Work/ Literary Review}
There is a wealth of previous work pertaining to how interaction design concepts specifically map to the usability of modern display technology.

Some ``Interaction on touch sensitive screens is literally the most `direct' form of HCI, where information display and control are but one surface. The zero displacement between input and output, control and feedback, hand action and eye gaze, make touch screens very intuitive to use, particularly for novice users. Not surprisingly, touch screens have been widely and successfully used in public information kiosks, ticketing machines, bank teller machines, and the like. Besides its directness, touch screen interfaces also have additional advantages. First, because its control surface is overlaid on the display, no extra input control device or space is necessary for touch screen interaction. Second, touch screens are more robust than free moving input devices such as the mouse. Being direct between control and display, touch screens also have special limitations. First, the user's finger, hand, and arm can obscure part of the screen. Second, the human finger as a pointing device has a very low 'resolution'." \cite{Apple} (High Precision Touch Screen Interaction)

@@

\begin{figure}
\centering
\includegraphics[width=2in]{space.jpg}

\caption{A sample figure}
\label{figure-sample}
\end{figure}

@@

Wrap up your paper with an ``executive summary'' of the paper itself, reiterating its subject and its major points.  If you want examples, just look at the conclusions from the literature.

>>>>

The study of electronic screens is significant in the field of human-computer interaction (HCI) as screens are the devices through which information is transferred between the users and the interface. Although electronic displays have been around for nearly a century,\footnote{The cathode ray tube (CRT) was first made commercial in 1922.\cite{Cathode}} they are still transforming and evolving in a multitude of ways. Screens are diversifying in order to tackle the limitations that have presented themselves over the years.

Screen devices have been changing in size, shape, flexibility, and resolution in order to improve usability for specific tasks. For example, \textit{focus plus context screens}, which are wall-size low-resolution displays with an embedded high-resolution display region, are currently a proposed solution to working with visual documents too large to fit standard screens.\cite{Baudisch} Another kind of screen that is emerging is the \textit{BiDirectional (BiDi) Screen}, which is a thin, depth-sensing liquid-crystal display (LCD) that allows for 3D interaction using light fields.\cite{Hirsch}

 Though each kind of screen has its merits, this study will focus exclusively on touch sensitive screens. Many experts within the field of interaction design have discussed how the concepts of interaction design map specifically to the usability of touch sensitive screens. In a study from Link\"{o}ping University, researchers articulated how ``interaction design on touch sensitive screens is literally the most `direct' form of HCI, where information display and control are but one surface."\cite{Albinsson}

\section{Background/ Prior Work/ Literary Review}
There exists a fair amount of previous work pertaining to the advantages as well as the limitations of touch sensitive screens. One limitation that is often discussed in the literature is how typing on flat surfaces with no physical keys to guide the fingers requires heightened visual attention to avoid typos. A study by Hussain Tinwala and Scott MacKenzie suggests that since the visual demand on the user is increased, concentration is diverted from the thoughts being expressed. \cite{Tinwala:2010:ETE:1868914.1868972} Be that as it may, there exist several text entry methods that attempt to address this problem. For instance, Tinwala and MacKenzie present a system that includes auditory and tactile feedback to guide eyes-free entry using speech and non-speech sounds, and by vibrations. \cite{Tinwala:2010:ETE:1868914.1868972} Another proposed solution comes from Tactus Technology, a company in Fremont, California. Employees of Tactus Technology are creating a keyboard with shape-shifting keys that pop up from the screen's surface when needed and recede again when no longer necessary.\cite{Tactus}
\begin{figure}[ht]
\centering
\includegraphics[width=2.7in]{tactus-keyboard.jpg}

\caption{A Tactus keyboard}
\label{figure-sample}
\end{figure}

Some ``Interaction on touch sensitive screens is literally the most `direct' form of HCI, where information display and control are but one surface. The zero displacement between input and output, control and feedback, hand action and eye gaze, make touch screens very intuitive to use, particularly for novice users. Not surprisingly, touch screens have been widely and successfully used in public information kiosks, ticketing machines, bank teller machines, and the like. Besides its directness, touch screen interfaces also have additional advantages. First, because its control surface is overlaid on the display, no extra input control device or space is necessary for touch screen interaction. Second, touch screens are more robust than free moving input devices such as the mouse. Being direct between control and display, touch screens also have special limitations. First, the user's finger, hand, and arm can obscure part of the screen. Second, the human finger as a pointing device has a very low 'resolution'."

@@

@@

Wrap up your paper with an ``executive summary'' of the paper itself, reiterating its subject and its major points.  If you want examples, just look at the conclusions from the literature.
\clearpage
